% English content for the CV
% To add a new section label or piece of content, define a new \def macro here.

% Locale
\def\country{Sofia, Bulgaria}
\def\lastupdatedtext{Last Updated on}

% ── Education ─────────────────────────────────────────────────────────────────
\def\education{Education}

\def\educationMSName{MSc Space Engineering \newline and Technology}
\def\educationMSLocation{National Institute \newline for Space Research (INPE)}
\def\educationMSDuration{2018 – 2021 | São José dos Campos, BR}
\def\educationMSArea{Space Systems Engineering \& Management}

\def\educationBSName{BS Software Engineering}
\def\educationBSLocation{Federal University of Goiás (UFG)}
\def\educationBSDuration{2013 – 2016 | Goiânia, BR}

% ── Skills ────────────────────────────────────────────────────────────────────
\def\skills{Skills}
\def\software{Software}
\def\softwareProfessional{Professional}
\def\softwareProjects{Projects}
\def\softwareHobby{Hobby}

\def\skillsProfessionalList{%
Python \textbullet{} Java \textbullet{} Bash \textbullet{} SQL \\
Docker \textbullet{} Git \textbullet{} Linux \textbullet{} REST APIs%
}
\def\skillsProjectsList{%
C \textbullet{} C++ \textbullet{} ReactJS \textbullet{} R \textbullet{} \LaTeX%
}
\def\skillsHobbyList{%
Rust \textbullet{} Neovim \textbullet{} Fish Shell%
}

% ── Languages ─────────────────────────────────────────────────────────────────
\def\languages{Languages}
\def\languagesEN{English: Fluent — TOEFL IBT 107}
\def\languagesFR{French: Intermediate}
\def\languagesJP{Japanese: JLPT N5}
\def\languagesPT{Portuguese: Native}

% ── Professional Experience ───────────────────────────────────────────────────
\def\professional{Professional Experience}

% EnduroSat – Mission Operations Technical Lead
\def\professionalESTLTitle{Mission Operations Technical Lead}
\def\professionalESTLDur{Feb 2025 – Present | Sofia, BG (Remote)}
\def\professionalESTLDesc{%
\begin{tightemize}
\item Lead mission operations for a commercial satellite fleet, owning technical standards, procedures, and tooling strategy.
\item Bridge engineering and operations to drive spacecraft lifecycle decisions and anomaly resolution.
\item Mentor mission operators and coordinate cross-team efforts across multiple concurrent missions.
\end{tightemize}%
}

% EnduroSat – Mission Operator
\def\professionalESMOTitle{Mission Operator}
\def\professionalESMODur{Mar 2023 – Feb 2025 | Sofia, BG (Remote)}
\def\professionalESMODesc{%
\begin{tightemize}
\item Executed satellite mission operations: maneuver planning, payload commanding, and anomaly diagnosis.
\item Authored and maintained operational runbooks and contingency procedures for mission-critical activities.
\end{tightemize}%
}

% EnduroSat – Software Engineer
\def\professionalESSETitle{Software Engineer}
\def\professionalESSEDur{Apr 2021 – Mar 2023 | Sofia, BG (Remote)}
\def\professionalESSEDesc{%
\begin{tightemize}
\item Built and maintained ground segment software for satellite telemetry processing and mission planning.
\item Developed monitoring dashboards and data pipelines for real-time satellite health assessment.
\end{tightemize}%
}

% Earlier experience (condensed)
\def\professionalEarlyTitle{Earlier Experience}
\def\professionalEarlyDur{2015 – 2021}
\def\professionalEarlyDesc{%
\begin{tightemize}
\item Software engineering roles at MediaLab/UFG, Fitsmind (Norway, remote), ZG Soluções, and i9 Tecnologia — full-stack development across Java, Ruby on Rails, Grails, and JavaScript.
\end{tightemize}%
}

% ── Research ──────────────────────────────────────────────────────────────────
\def\research{Research}
\def\researchMS{Full-Time Master's Researcher}
\def\researchMSDur{2018 – 2021 | São José dos Campos, BR}
\def\researchMSDesc{%
Developed Big Data analysis tools and algorithms to support operators at Brazil's Satellite Control Center (CCS/INPE).
CAPES scholarship recipient.%
}

% ── Publications ──────────────────────────────────────────────────────────────
\def\publications{Publications}
